\begin{draft}
\section{Kit Services}

\subsection{Philosophy}

The purpose of the Student Robotics Competition Programme is to foster interest in engineering. However, the vast majority of competitors will never have engineered any software, mechanics or electronics. Asking them to build a robot from scratch, without support in each of these areas, would not help. It would not be an enjoyable experience and may even have the opposite effect to that desired.

To support teams in the three key areas of mechanical, electronic and software we provide them with a kit. The purpose of this kit is to make it feasible for completely inexperienced teams to build robots capable of competing in the Competition. It is expected that some teams will develop robots using more than the provided kit and this is encouraged if their mentor feels that they have the necessary capabilities and experience.

Teams are not required to use the kit to compete. They may build their robot using whatever materials they desire, provided that they, and the final robot, are safe. In some situations teams may have to get prior approval from Student Robotics regarding use of certain non-kit parts. Any approval requirements will be detailed in the rules provided to teams at Kickstart. \emph{TODO: link to section}

\subsubsection{Minimum Viable Robot}

The kit provided by Student Robotics must provide teams with all of the parts, both physical and virtual, to allow them to easily construct a Minimum Viable Robot (MVR) - a robot which is capable of competing within the game. This MVR significantly lowers the barrier to entry and also allows teams to focus on the elements of their robot that interest them the most. The MVR will allow them to compete, but their own original work is what will help them to win.

The process for assembling the kit into an MVR must be straightforward. It should require a similar level of skill as is required to assemble a piece of flatpack furniture. This will allow teams to rapidly obtain a robot with which they could compete.

Building the MVR is a significant milestone for a team. At this point they are ready to compete. After this point teams should be strongly encouraged to maintain this state as they develop their robot further. At any point in time after this it should take very little effort to present a robot that is suitable for use in the Competition.

The kit should not be designed with the sole purpose of building the MVR in mind. It should consist of composable modules that can be used by teams designing a robot from scratch. The MVR is just one combination of these modules and does not necessarily use all of the kit in its construction.

\subsubsection{Kit Requirements}

As well as allowing an MVR to be constructed the Kit should meet some other general criteria. It should be:

\begin{enumerate}
  \item Enjoyable for teams to use.
  \item As close to the state of the art as possible.
  \item Be rugged and robust to accidental damage.
  \item Consist of commercial off the shelf parts where appropriate.
\end{enumerate}

These requirements help to ensure that the Kit has significant value to teams while ensuring that the cost to Student Robotics is reasonable.

\subsection{Development}

To meet our requirement of providing teams with a Kit all parts of it must be developed before being handed to teams. This development includes the design and creation of new pieces of hardware and software and the research and evaluation of existing hardware and software prior to inclusion in the Kit. The \role{hw-dev-coord} and \role{kit-sw-coord} are responsible for the development of the hardware and software parts of the kit respectively, however the \role{kit-coord} is ultimately responsible for deciding what is included in the Kit.

The Kit itself consists of many parts. These parts fall into the following categories: electronic hardware, mechanical hardware, local software and remote software. Some parts of the kit are considered to be more critical than others and this is represented in the relevant development processes documented below.

To aid Student Robotics volunteers in the development of the Kit Development Kits are available. A Development Kit is identical to that provided to teams, but is reserved specifically for the purpose of development. There are also development tools available such as programmers and test jigs. The \role{kit-coord} is responsible for the allocation of Development Kits and tools. The \role{kit-logistics-coord} is responsible for the storage, tracking and shipping of Development Kits and tools.

\subsubsection{Electronic and Mechanical Hardware}

The development of electronic and mechanical parts of the kit is considered to be a very critical process, since they can only be changed once per Competition Programme Year. For this reason the process is somewhat more formal and rigorous than that of other kit parts, such as remote software. The desired outcome of this process is hardware that is robust, reliable and useful to teams.

Upon completion of development of a new part it is expected that, along with all of the design files, documentation is provided for manufacturing, maintenance and use. Any new parts that require firmware to function must, as a minimum, have firmware that allows for remote updating.

As in all engineering there are many conflicting factors to be optimised in the design of kit parts. While developing electronic and mechanical parts it is useful to keep the following factors in mind: ease of manufacture, ease of end of line test, ease of annual test, ease of use, ease of repair, robustness and cost. Note that these are in no particular order and all are important.

Money is available to support the development and prototyping of new electronic and mechanical kit parts. It is also available to support the development of Kit related tools, such as test jigs. Before any money is allocated towards development a Kit Part Development Proposal must be reviewed and accepted by the \role{hw-dev-coord}. No money should be spent towards kit development with an expectation of reimbursement without an accepted Kit Part Development Proposal. Where a proposal has been accepted and money allocated, it is the responsibility of the named lead developer to ensure that the budget is not exceeded. The lead developer should be constant communication with the \role{hw-dev-coord} throughout the development process.

The submission of a Kit Part Development Proposal is required when starting to develop a new electronic part, mechanical part or tool. The purpose of this proposal is twofold: it helps to ensure people don't waste their time and effort developing something that has little chance of being included in the Kit and it acts as a request for money to help with the development of the part. It is strongly advised that one talks to the \role{hw-dev-coord} before writing a proposal.

A Kit Part Development Proposal must include:
\begin{itemize}
  \item The name of the lead developer.
  \item A description of the item, including whether it is an electronic part, mechanical part or tool for internal use.
  \item The functionality it provides to teams (if applicable).
  \item Example user stories to allow later assessment of suitability to fulfil requirements.
  \item An estimate of the development time required.
  \item A development plan showing design review points.
  \item If proposing the development of bespoke hardware, a review of COTS products providing similar functionality and reasons why these are not suitable.
  \item The estimated development cost.
  \item The estimated production cost per kit/per tool.
  \item The estimated annual maintenance cost per kit, including consumable parts (if applicable).
\end{itemize}

An example Kit Part Development Proposal can be found in Appendix \emph{TODO: write example KPDP}.

Once development is complete a Kit Addition Proposal must be submitted to the \role{kit-coord}. This Kit Addition Proposal acts as a final check of suitability before manufacturing/purchasing commences and the developed part is included in the Kit (or, in the case of newly developed tools, added to the set of development tools available) . The proposal must include:
\begin{itemize}
  \item A review of the original Kit Part Development Proposal showing how the developed part fulfils the user stories and provides the functionality specified.
  \item Links to the source of the hardware/software developed including any new documentation.
  \item A reviewed estimated production cost per kit/per tool. This will be more accurate than the initial estimate due to the design being complete.
  \item A reviewed annual maintenance cost per kit (if applicable).
  \item A manufacturing plan. If the new part is not fully manufactured, tested and entered into the inventory before the manufacturing deadline then it will not ship in the next competition year. \emph{TODO: link to manufacturing deadline}.
\end{itemize}

An example Kit Addition Proposal can be found in Appendix \emph{TODO: write example KAP}.

\subsubsection{Kit Local Software}
\subsubsection{Kit Remote Software}

\subsection{Manufacture}

\subsection{Life Cycle}

\subsection{Licensing}

\begin{enumerate}

\item Development Process
  \begin{enumerate}
    \item Kit local software
      \begin{enumerate}
        \item Kit local software includes all software, written and maintained by SR, that runs on components of the kit. This includes firmware.
        \item The development of kit local software is considered to be less critical than that of the electronic and mechanical hardware since in the majority of cases it can be updated during the competition year.
        \item A very small amount of kit local software cannot be updated during the competition year, for example bootloaders. The \role{kit-sw-coord} is responsible for defining which software is highly critical. Changes to this highly critical software must be reviewed and approved by the \role{kit-sw-coord}.
      \end{enumerate}
    \item Kit remote software
      \begin{enumerate}
        \item Kit remote software includes all software, written and maintained by SR, that is used by teams in the process of developing their robot that does not run on the components of the kit.
        \item The development of kit remote software is the least critical of all kit components since it is reasonably trivial to update it throughout the year.
        \item Before starting development of a new feature or piece of software the \role{kit-sw-coord} should be consulted to ensure that it will be useful and how it may be incorporated into the existing infrastructure.
        \item All kit remote software should provide an API. The API should be the only way that other SR software interacts it. It should be expected that teams will be using the API.
      \end{enumerate}
    \item General software development
      \begin{enumerate}
        \item Each piece of software, as defined by the \role{kit-sw-coord}, must maintain the following documentation alongside the source code:
          \begin{enumerate}
            \item A description of the piece of software, including its scope and how/where it will interface with existing software.
            \item Any potential legal implications.
          \end{enumerate}
        \item Prior to the release of a new version of the software the \role{kit-coord} must verify that there are no new potential legal implications due to the new features and that all of the existing potential legal implications have been suitably dealt with.
        \item APIs of all kit software must remain stable for the duration of the Competition Programme Year. That is, from Kickstart to the kit return deadline.
        \item API stability is defined as:
          \begin{enumerate}
            \item Methods/interfaces must not be renamed without providing a backwards compatible alias.
            \item The functionality of methods/interfaces must remain the same.
            \item New methods/interfaces must not affect the functionality of existing methods/interfaces.
          \end{enumerate}
      \end{enumerate}
  \end{enumerate}

\item Manufacture
  \begin{enumerate}
    \item Responsibility of \role{hw-prod-coord} to get newly developed bits of kit manufactured/purchased ready for inclusion in the kit.
    \item Also need to manufacture new whole kits when increasing number of teams.
    \item Manufacturing only really applicable to electronic/mechanical kit components.
    \item Newly manufactured or purchased kit must be entered into the inventory.
    \item Kit being manufactured or purchased for the next Competition Programme Year must be ready for packing at least 2 weeks before the Kit Packing Event (TODO: link to section).
  \end{enumerate}

\item Production
  \begin{enumerate}
  \item Support
    \begin{enumerate}
      \item \role{kit-support-coord} provides Kit support to teams and other users of the Kit.
      \item Team support is primarily provided via the Forum.
    \end{enumerate}
  \item Inventory
    \begin{enumerate}
      \item Physical items of the kit are tracked in the Inventory. Each item is known as an asset.
      \item The Inventory allows for the condition (working, broken, unknown), location and other information of an asset to be recorded.
      \item All historic information for an asset is recorded.
      \item Each asset in the Inventory is identified with a unique asset code.
      \item The asset code is marked on the physical item either with a printed sticker or written by hand. (The preference is for a printed sticker that has both human and machine readable markings).
      \item Anyone (\emph{TODO: not actually anyone, need to define who}) may update the Inventory as assets are moved or their state changes. However the \role{kit-logistics-coord} is responsible for ensuring that the Inventory is a good representation of reality.
      \item When assets are disposed of the \role{kit-logistics-coord} is responsible for removing them from the Inventory.
      \item The Inventory also tracks some non-kit assets. These can be broken down into the following categories:
        \begin{enumerate}
          \item Kit development - tools and hardware for developing and testing the kit.
          \item Competition hardware - items such as arena walls and display computers. These are \textbf{only} for use at the competition and at no other event.
          \item Game hardware - the same types of assets as competition hardware but available for use throughout the year such as at tech days.
          \item General event hardware - items for use at all types of SR event.
          \item Miscellaneous - the small number of assets not covered by the above categories.
        \end{enumerate}
      \item The \role{kit-logistics-coord} is also responsible for the storage and shipping of non-kit assets in the Inventory.
    \end{enumerate}
  \item Kit lifecycle
    \begin{enumerate}
      \item Competition Programme Year
        \begin{enumerate}
          \item During the Competition Programme Year the Production Kit is in the hands of teams.
          \item Teams collect their kit at a Kickstart event.
          \item Teams who cannot attend a Kickstart event must arrange for a courier to collect their kit when instructed to do so by their \role{local-team-coord}. The \role{kit-coord} will advise \roletitle{local-team-coord}s of the necessary details when available.
          \item The \role{kit-logistics-coord} is responsible for ensuring that kits for couriering to teams are available for collection no later than 2 weeks after Kickstart.
        \end{enumerate}
      \item Kit Collation Event
        \begin{enumerate}
          \item An annual multi-day event that ocurrs in July.
          \item All of the kits from the preceding Competition Programme Year are split into their constituent parts.
          \item The state of each piece of kit is assessed. Where applicable testing is carried out to verify the state.
          \item The Inventory is updated as the process progresses.
          \item The event must take place in a geographically central location.
          \item The event must be announced to volunteers at least 4 weeks prior to its date.
          \item Volunteers must register to attend to allow for work processes to be organised. They do not have to attend for both days.
          \item The venue must allow for the kit to be left in the workspace overnight. The workspace must be lockable.
          \item The \role{hw-prod-coord} is responsible for running the event.
        \end{enumerate}
      \item Kit Packing Event
        \begin{enumerate}
          \item An annual multi-day event that occurs in August at least four weeks after the Kit Collation Event. It must occur at least four weeks prior to Kickstart.
          \item All of the kits for the following Competition Programme Year are packed ready for Kickstart.
          \item The Inventory is updated as the process progresses.
          \item The venue, announcement and registration requirements are the same as the Kit Collation Event requirements.
          \item The \role{hw-prod-coord} is responsible for running the event.
        \end{enumerate}
      \item Kit repair
        \begin{enumerate}
          \item Kit found to be faulty at the Kit Collation Event or otherwise known to be faulty should be repaired where possible.
          \item Any repairs must be completed prior to the Kit Packing Event.
          \item If a particular asset is beyond repair then a replacement must be purchased prior to the Kit Packing Event. In the case of SR custom electronics hardware replacements must be manufactured in the next manufacturing run.
        \end{enumerate}
    \end{enumerate}
  \end{enumerate}

\item Licensing requirements
  \begin{enumerate}

  \item The following must be licensed under a GPL-compatible license, as qualified by the \href{http://www.gnu.org/licenses/license-list.en.html#GPLCompatibleLicenses}{Free Software Foundation}:
    \begin{enumerate}
    \item All software distributed as part of the SR kit.
    \item All software executed on all servers run by SR. (Note that this does not include software run on third-party servers -- e.g. github.com -- for obvious reasons.)
    \end{enumerate}

  \item The designs of all hardware that is manufactured by SR for the kit must be licensed under at least one of the following licenses:
    \begin{enumerate}
    \item The Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International license
    \item The Creative Commons Attribution-ShareAlike 4.0 International license
    \end{enumerate}
  \end{enumerate}


\item Requirements for kit shipping
  \begin{enumerate}
    \item{Whole kits are to be shipped in the container that they are provided in.}
    \item{Batteries in battery bags}
    \item{\pounds500 insurance on whole-kit shipping}
    \item{Battery courier instructions (approved list, labels, etc)}
    \item{Link Kit Return section here when written.}
  \end{enumerate}
\item Policy on kit replacement
  \begin{enumerate}
    \item{\role{kit-logistics-coord} responsible for shipping replacement parts after request/authorisation from \role{kit-support-coord}.}
    \item{\role{local-team-coord} responsible for reporting broken/damaged kit to \role{kit-support-coord} for replacement.}
    \item{Any piece of kit replaced free-of-charge when damaged accidentally.}
    \item{Any piece of kit, except for batteries, replaced free-of-charge when damaged due to misuse/negligence in the first instance. Teams charged for further damage due to misuse/negligence.}
    \item{In the case of batteries damaged due to misuse/negligence no replacements will be provided and teams must dispose of the battery in question.}
  \end{enumerate}

\item Classes of kit
  \begin{enumerate}
    \item There are multiple classes of kit that fulfil distinct requirements. For each class a specific role is responsible for the allocation of said kits. For all classes of kit the \role{kit-logistics-coord} is responsible for the storage, tracking and shipping of the kits at all times. The classes are as follows:
      \begin{enumerate}
        \item Production kit. This is the kit used by teams. The \role{team-coord} is responsible for allocation.
        \item Spare kit. This is kit ready to be shipped to teams as replacements. The \role{kit-support-coord} is responsible for allocation.
        \item Development kit. This is kit used by the development team.  The \role{kit-coord} is responsible for allocation.
        \item Support kit. This is kit used by the support team to help teams and internal users of the kit with issues. The \role{kit-support-coord} is responsible for allocation.
        \item PR kit. This is kit available for public relations/exhibition use. The \role{pr-coord} is responsible for allocation.
        \item Local kit. This is kit available to \role{local-team-coord}s for training and occasional PR/advertising use. It may also be used at Tech Days to provide hands-on support. The \role{team-coord} is responsible for allocation.
      \end{enumerate}
    \item There are enough production kits to cater for the number of teams taking part in the competition programme.
    \item After a manufacturing run there are at least 0.125 times the number of teams of spare kits available. As non-spare kit components get replaced the number of spares will reduce. It is the responsibility of the \role{hw-prod-coord} to ensure that spare kit components are replenished in due course.
    \item The \role{kit-coord} is responsible for defining the quantity of development, support, pr and local kits. They may change the class of a given kit as they see fit.
    \item It is the responsibility of the \role{hw-prod-coord} to ensure that enough kits exist. Specifically the \role{hw-prod-coord} needs to ensure that there are more kits manufactured in preparation for the next competition programme year.
  \end{enumerate}
\end{enumerate}
\end{draft}
