%\begin{draft} in kickstart.tex
\section{Tech Days}

\begin{itemize}
\item What a tech day is:
  \begin{itemize}
  \item Opportunity for teams to work on their robot for a full working day.  Teams generally work on them for 1 or 2 hours a week normally.
  \item Teams come to us, rather than mentors to team.
  \item Teams meet other teams.
  \end{itemize}


\item What should happen at tech days:
  \begin{itemize}
  \item Tech days should generally run from 9 or 10 AM to 4 or 5 PM.
  \item Teams must be provided with:
    \begin{itemize}
    \item Internet access
    \item Toilet facilities
    \item Table space, chairs.
    \item Refreshments: Water at a minimum.  SR volunteers must not be in the position of providing hot drinks: must be done by third party.
    \end{itemize}
  \end{itemize}

\item Some volunteers (\textit{how many!?}) must be present to assist teams -- these volunteers must meet the same criteria that apply to mentors.

\item  Organising the tech day:
  \begin{itemize}
  \item Provide advance notice to teams of at least 8 weeks.  PR must be informed too.
  \item Where possible provide parking and inform teams of the availability or lack of parking as appropriate.
  \item Provide template risk assessment for teachers.
  \item Perform risk assessment.
  \item Date selection:
    \begin{itemize}
    \item Must be on a weekend, or alternatively a weekday in a school holiday, or bank holiday.
    \item Ensure that enough volunteers can attend.
    \end{itemize}
  \item Teams must register to attend.  \textit{How?}
  \end{itemize}

\end{itemize}
\end{draft}
